AirBNB Data Preparation and Imputation

### 2016-11-22 abbDataPrep_Script.Rmd
remove unnecessary source()
updating path code

@@

@@

  source("c:/code/datamgmttools/dataMungetools.R")
  source("c:/code/research/airbnbMelbourne/dataPrep_Functions.R")

>>>>

  # Get computer names
  comp.name <- Sys.info()['nodename']

  # Assign path based on computer name
  if(comp.name == '7020D-121777-W' | 
      comp.name == 'DESKTOP-1D7JO4J'){

@@

  } else {

      data.path <- 'gideon path'

  }

@@

  source("c:/code/research/airbnbMelbourne/dataPrep_Functions.R")
